### 2018-08-08 paper/evaluation.tex

\subsubsection{Comparison to churnful Tor} % (fold)
\label{ssub:comparison_to_churnful_tor}

To demonstrate the need for \iac{SPOR}, 
we attempt the same experiment as before, but this time using an availability threshold $\theta = 1$ (cf~\ref{SPOR}): 
layers only contain one random descriptor.
Over 5 experiments, we observed a file transfer success rate of 41.7\%, which is far below our results when leveraging on \ac{SPOR}.

>>>>

% \subsubsection{Comparison to churnful Tor} % (fold)
% \label{ssub:comparison_to_churnful_tor}

To get a rough baseline to evaluate the need for \iac{SPOR}, 
we attempt the same experiment as before, but this time using an availability threshold $\theta = 1$ (cf~\ref{SPOR}): 
layers only contain one random descriptor, as a naive approximation of
classical \acl{OR}. 
Over 5 experiments, we observed a file transfer success rate of 41.7\%, which is far below our results when leveraging on \ac{SPOR}.
